### 2022-10-13 cvpr2023/latex/PaperForReview.tex
Add files via upload

% CVPR 2023 Paper Template
% based on the CVPR template provided by Ming-Ming Cheng (https://github.com/MCG-NKU/CVPR_Template)
% modified and extended by Stefan Roth (stefan.roth@NOSPAMtu-darmstadt.de)

\documentclass[10pt,twocolumn,letterpaper]{article}

%%%%%%%%% PAPER TYPE  - PLEASE UPDATE FOR FINAL VERSION
\usepackage[review]{cvpr}      % To produce the REVIEW version
%\usepackage{cvpr}              % To produce the CAMERA-READY version
%\usepackage[pagenumbers]{cvpr} % To force page numbers, e.g. for an arXiv version

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}

% It is strongly recommended to use hyperref, especially for the review version.
% hyperref with option pagebackref eases the reviewers' job.
% Please disable hyperref *only* if you encounter grave issues, e.g. with the
% file validation for the camera-ready version.
%
% If you comment hyperref and then uncomment it, you should delete
% ReviewTempalte.aux before re-running LaTeX.
% (Or just hit 'q' on the first LaTeX run, let it finish, and you
%  should be clear).
\usepackage[pagebackref,breaklinks,colorlinks]{hyperref}

% Support for easy cross-referencing
\usepackage[capitalize]{cleveref}
\crefname{section}{Sec.}{Secs.}
\Crefname{section}{Section}{Sections}
\Crefname{table}{Table}{Tables}
\crefname{table}{Tab.}{Tabs.}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{*****} % *** Enter the CVPR Paper ID here
\def\confName{CVPR}
\def\confYear{2023}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
%\title{\LaTeX\ Author Guidelines for \confName~Proceedings}
\title{A Dataset for Auxiliary Depression Diagnosis based on Gait}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}
\maketitle

%%%%%%%%% ABSTRACT
\begin{abstract}
   The ABSTRACT is to be in fully justified italicized text, at the top of the left-hand column, below the author and affiliation information.
   Use the word ``Abstract'' as the title, in 12-point Times, boldface type, centered relative to the column, initially capitalized.
   The abstract is to be in 10-point, single-spaced type.
   Leave two blank lines after the Abstract, then begin the main text.
   Look at previous CVPR abstracts to get a feel for style and length.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
\label{sec:intro}

Please follow the steps outlined below when submitting your manuscript to the IEEE Computer Society Press.
This style guide now has several important modifications (for example, you are no longer warned against the use of sticky tape to attach your artwork to the paper), so all authors should read this new version.

%-------------------------------------------------------------------------
\subsection{Language}

All manuscripts must be in English.

\subsection{Dual submission}

Please refer to the author guidelines on the \confName\ \confYear\ web page for a
discussion of the policy on dual submissions.

\subsection{Paper length}
Papers, excluding the references section, must be no longer than eight pages in length.
The references section will not be included in the page count, and there is no limit on the length of the references section.
For example, a paper of eight pages with two pages of references would have a total length of 10 pages.
{\bf There will be no extra page charges for \confName\ \confYear.}

Overlength papers will simply not be reviewed.
This includes papers where the margins and formatting are deemed to have been significantly altered from those laid down by this style guide.
Note that this \LaTeX\ guide already sets figure captions and references in a smaller font.
The reason such papers will not be reviewed is that there is no provision for supervised revisions of manuscripts.
The reviewing process cannot determine the suitability of the paper for presentation in eight pages if it is reviewed in eleven.

%-------------------------------------------------------------------------
\subsection{The ruler}
The \LaTeX\ style defines a printed ruler which should be present in the version submitted for review.
The ruler is provided in order that reviewers may comment on particular lines in the paper without circumlocution.
If you are preparing a document using a non-\LaTeX\ document preparation system, please arrange for an equivalent ruler to appear on the final output pages.
The presence or absence of the ruler should not change the appearance of any other content on the page.
The camera-ready copy should not contain a ruler.
(\LaTeX\ users may use options of cvpr.sty to switch between different versions.)

Reviewers:
note that the ruler measurements do not align well with lines in the paper --- this turns out to be very difficult to do well when the paper contains many figures and equations, and, when done, looks ugly.
Just use fractional references (\eg, this line is $087.5$), although in most cases one would expect that the approximate location will be adequate.

\subsection{Paper ID}
Make sure that the Paper ID from the submission system is visible in the version submitted for review (replacing the ``*****'' you see in this document).
If you are using the \LaTeX\ template, \textbf{make sure to update paper ID in the appropriate place in the tex file}.

\subsection{Mathematics}

Please number all of your sections and displayed equations as in these examples:
\begin{equation}
  E = m\cdot c^2
  \label{eq:important}
\end{equation}
and
\begin{equation}
  v = a\cdot t.
  \label{eq:also-important}
\end{equation}
It is important for readers to be able to refer to any particular equation.
Just because you did not refer to it in the text does not mean some future reader might not need to refer to it.
It is cumbersome to have to use circumlocutions like ``the equation second from the top of page 3 column 1''.
(Note that the ruler will not be present in the final copy, so is not an alternative to equation numbers).
All authors will benefit from reading Mermin's description of how to write mathematics:
\url{http://www.pamitc.org/documents/mermin.pdf}.

\subsection{Blind review}

Many authors misunderstand the concept of anonymizing for blind review.
Blind review does not mean that one must remove citations to one's own work---in fact it is often impossible to review a paper unless the previous citations are known and available.

Blind review means that you do not use the words ``my'' or ``our'' when citing previous work.
That is all.
(But see below for tech reports.)

Saying ``this builds on the work of Lucy Smith [1]'' does not say that you are Lucy Smith;
it says that you are building on her work.
If you are Smith and Jones, do not say ``as we show in [7]'', say ``as Smith and Jones show in [7]'' and at the end of the paper, include reference 7 as you would any other cited work.

An example of a bad paper just asking to be rejected:
\begin{quote}
\begin{center}
    An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of our previous paper [1], and show it to be inferior to all previously known methods.
   Why the previous paper was accepted without this analysis is beyond me.

   [1] Removed for blind review
\end{quote}

An example of an acceptable paper:
\begin{quote}
\begin{center}
     An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of the  paper of Smith \etal [1], and show it to be inferior to all previously known methods.
   Why the previous paper was accepted without this analysis is beyond me.

   [1] Smith, L and Jones, C. ``The frobnicatable foo filter, a fundamental contribution to human knowledge''. Nature 381(12), 1-213.
\end{quote}

If you are making a submission to another conference at the same time, which covers similar or overlapping material, you may need to refer to that submission in order to explain the differences, just as you would if you had previously published related work.
In such cases, include the anonymized parallel submission~\cite{Authors14} as supplemental material and cite it as
\begin{quote}
[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324, Supplied as supplemental material {\tt fg324.pdf}.
\end{quote}

Finally, you may feel you need to tell the reader that more details can be found elsewhere, and refer them to a technical report.
For conference submissions, the paper must stand on its own, and not {\em require} the reviewer to go to a tech report for further details.
Thus, you may say in the body of the paper ``further details may be found in~\cite{Authors14b}''.
Then submit the tech report as supplemental material.
Again, you may not assume the reviewers will read this material.

Sometimes your paper is about a problem which you tested using a tool that is widely known to be restricted to a single institution.
For example, let's say it's 1969, you have solved a key problem on the Apollo lander, and you believe that the CVPR70 audience would like to hear about your
solution.
The work is a development of your celebrated 1968 paper entitled ``Zero-g frobnication: How being the only people in the world with access to the Apollo lander source code makes us a wow at parties'', by Zeus \etal.

You can handle this paper like any other.
Do not write ``We show how to improve our previous work [Anonymous, 1968].
This time we tested the algorithm on a lunar lander [name of lander removed for blind review]''.
That would be silly, and would immediately identify the authors.
Instead write the following:
\begin{quotation}
\noindent
   We describe a system for zero-g frobnication.
   This system is new because it handles the following cases:
   A, B.  Previous systems [Zeus et al. 1968] did not  handle case B properly.
   Ours handles it by including a foo term in the bar integral.

   ...

   The proposed system was integrated with the Apollo lunar lander, and went all the way to the moon, don't you know.
   It displayed the following behaviours, which show how well we solved cases A and B: ...
\end{quotation}
As you can see, the above text follows standard scientific convention, reads better than the first version, and does not explicitly name you as the authors.
A reviewer might think it likely that the new paper was written by Zeus \etal, but cannot make any decision based on that guess.
He or she would have to be sure that no other authors could have been contracted to solve problem B.
\medskip

\noindent
FAQ\medskip\\
{\bf Q:} Are acknowledgements OK?\\
{\bf A:} No.  Leave them for the final copy.\medskip\\
{\bf Q:} How do I cite my results reported in open challenges?
{\bf A:} To conform with the double-blind review policy, you can report results of other challenge participants together with your results in your paper.
For your results, however, you should not identify yourself and should not mention your participation in the challenge.
Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\

\begin{figure}[t]
  \centering
  \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}

   \caption{Example of caption.
   It is set in Roman so that mathematics (always set in Roman: $B \sin A = A \sin B$) may be included without an ugly clash.}
   \label{fig:onecol}
\end{figure}

\subsection{Miscellaneous}

\noindent
Compare the following:\\
\begin{tabular}{ll}
 \verb'$conf_a$' &  $conf_a$ \\
 \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
\end{tabular}\\
See The \TeX book, p165.

The space after \eg, meaning ``for example'', should not be a sentence-ending space.
So \eg is correct, {\em e.g.} is not.
The provided \verb'\eg' macro takes care of this.

When citing a multi-author paper, you may save space by using ``et alia'', shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word).
If you use the \verb'\etal' macro provided, then you need not worry about double periods when used at the end of a sentence as in Alpher \etal.
However, use it only when there are three or more authors.
Thus, the following is correct:
   ``Frobnication has been trendy lately.
   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''

This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...'' because reference~\cite{Alpher03} has just two authors.

% Update the cvpr.cls to do the following automatically.
% For this citation style, keep multiple citations in numerical (not
% chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
% \cite{Alpher02,Alpher03,Authors14}.

\begin{figure*}
  \centering
  \begin{subfigure}{0.68\linewidth}
    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
    \caption{An example of a subfigure.}
    \label{fig:short-a}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.28\linewidth}
    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
    \caption{Another example of a subfigure.}
    \label{fig:short-b}
  \end{subfigure}
  \caption{Example of a short caption, which should be centered.}
  \label{fig:short}
\end{figure*}

%------------------------------------------------------------------------
\section{Formatting your paper}
\label{sec:formatting}

All text must be in a two-column format.
The total allowable size of the text area is $6\frac78$ inches (17.46 cm) wide by $8\frac78$ inches (22.54 cm) high.
Columns are to be $3\frac14$ inches (8.25 cm) wide, with a $\frac{5}{16}$ inch (0.8 cm) space between them.
The main title (on the first page) should begin 1 inch (2.54 cm) from the top edge of the page.
The second and following pages should begin 1 inch (2.54 cm) from the top edge.
On all pages, the bottom margin should be $1\frac{1}{8}$ inches (2.86 cm) from the bottom edge of the page for $8.5 \times 11$-inch paper;
for A4 paper, approximately $1\frac{5}{8}$ inches (4.13 cm) from the bottom edge of the
page.

%-------------------------------------------------------------------------
\subsection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must be kept
within a print area $6\frac{7}{8}$ inches (17.46 cm) wide by $8\frac{7}{8}$ inches (22.54 cm)
high.
%
Page numbers should be in the footer, centered and $\frac{3}{4}$ inches from the bottom of the page.
The review version should have page numbers, yet the final version submitted as camera ready should not show any page numbers.
The \LaTeX\ template takes care of this when used properly.

%-------------------------------------------------------------------------
\subsection{Type style and fonts}

Wherever Times is specified, Times Roman may also be used.
If neither is available on your word processor, please use the font closest in
appearance to Times to which you have access.

MAIN TITLE.
Center the title $1\frac{3}{8}$ inches (3.49 cm) from the top edge of the first page.
The title should be in Times 14-point, boldface type.
Capitalize the first letter of nouns, pronouns, verbs, adjectives, and adverbs;
do not capitalize articles, coordinate conjunctions, or prepositions (unless the title begins with such a word).
Leave two blank lines after the title.

AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
and printed in Times 12-point, non-boldface type.
This information is to be followed by two blank lines.

The ABSTRACT and MAIN TEXT are to be in a two-column format.

MAIN TEXT.
Type main text in 10-point Times, single-spaced.
Do NOT use double-spacing.
All paragraphs should be indented 1 pica (approx.~$\frac{1}{6}$ inch or 0.422 cm).
Make sure your text is fully justified---that is, flush left and flush right.
Please do not place any additional blank lines between paragraphs.

Figure and table captions should be 9-point Roman type as in \cref{fig:onecol,fig:short}.
Short captions should be centred.

\noindent Callouts should be 9-point Helvetica, non-boldface type.
Initially capitalize only the first word of section titles and first-, second-, and third-order headings.

FIRST-ORDER HEADINGS.
(For example, {\large \bf 1. Introduction}) should be Times 12-point boldface, initially capitalized, flush left, with one blank line before, and one blank line after.

SECOND-ORDER HEADINGS.
(For example, { \bf 1.1. Database elements}) should be Times 11-point boldface, initially capitalized, flush left, with one blank line before, and one after.
If you require a third-order heading (we discourage it), use 10-point Times, boldface, initially capitalized, flush left, preceded by one blank line, followed by a period and your text on the same line.

%-------------------------------------------------------------------------
\subsection{Footnotes}

Please use footnotes\footnote{This is what a footnote looks like.
It often distracts the reader from the main flow of the argument.} sparingly.
Indeed, try to avoid footnotes altogether and include necessary peripheral observations in the text (within parentheses, if you prefer, as in this sentence).
If you wish to use a footnote, place it at the bottom of the column on the page on which it is referenced.
Use Times 8-point type, single-spaced.

%-------------------------------------------------------------------------
\subsection{Cross-references}

For the benefit of author(s) and readers, please use the
{\small\begin{verbatim}
  \cref{...}
\end{verbatim}}  command for cross-referencing to figures, tables, equations, or sections.
This will automatically insert the appropriate label alongside the cross-reference as in this example:
\begin{quotation}
  To see how our method outperforms previous work, please see \cref{fig:onecol} and \cref{tab:example}.
  It is also possible to refer to multiple targets as once, \eg~to \cref{fig:onecol,fig:short-a}.
  You may also return to \cref{sec:formatting} or look at \cref{eq:also-important}.
\end{quotation}
If you do not wish to abbreviate the label, for example at the beginning of the sentence, you can use the
{\small\begin{verbatim}
  \Cref{...}
\end{verbatim}}
command. Here is an example:
\begin{quotation}
  \Cref{fig:onecol} is also quite important.
\end{quotation}

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times, single-spaced, at the end of your paper.
When referenced in the text, enclose the citation number in square brackets, for
example~\cite{Authors14}.
Where appropriate, include page numbers and the name(s) of editors of referenced books.
When you cite multiple papers at once, please make sure that you cite them in numerical order like this \cite{Alpher02,Alpher03,Alpher05,Authors14b,Authors14}.
If you use the template as advised, this will be taken care of automatically.

\begin{table}
  \centering
  \begin{tabular}{@{}lc@{}}
    \toprule
    Method & Frobnability \\
    \midrule
    Theirs & Frumpy \\
    Yours & Frobbly \\
    Ours & Makes one's heart Frob\\
    \bottomrule
  \end{tabular}
  \caption{Results.   Ours is better.}
  \label{tab:example}
\end{table}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.
In \LaTeX, avoid using the \texttt{center} environment for this purpose, as this adds potentially unwanted whitespace.
Instead use
{\small\begin{verbatim}
  \centering
\end{verbatim}}
at the beginning of your figure.
Please ensure that any point you wish to make is resolvable in a printed copy of the paper.
Resize fonts in figures to match the font in the body text, and choose line widths that render effectively in print.
Readers (and reviewers), even of an electronic copy, may choose to print your paper in order to read it.
You cannot insist that they do otherwise, and therefore must not assume that they can zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use \verb+\includegraphics+, and to specify the figure width as a multiple of the line width as in the example below
{\small\begin{verbatim}
   \usepackage{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.pdf}
\end{verbatim}
}

%-------------------------------------------------------------------------
\subsection{Color}

Please refer to the author guidelines on the \confName\ \confYear\ web page for a discussion of the use of color in your document.

If you use color in your plots, please keep in mind that a significant subset of reviewers and readers may have a color vision deficiency; red-green blindness is the most frequent kind.
Hence avoid relying only on color as the discriminative feature in plots (such as red \vs green lines), but add a second discriminative feature to ease disambiguation.

%------------------------------------------------------------------------
\section{Final copy}

You must include your signed IEEE copyright release form when you submit your finished paper.
We MUST have this form before your paper can be published in the proceedings.

Please direct any questions to the production editor in charge of these proceedings at the IEEE Computer Society Press:
\url{https://www.computer.org/about/contact}.

%%%%%%%%% REFERENCES
{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}

\end{document}

### 2022-10-17 cvpr2023/latex/PaperForReview - 副本.tex
Add files via upload

--- 2022-10-13 cvpr2023/latex/PaperForReview.tex
@@
 
-Please follow the steps outlined below when submitting your manuscript to the IEEE Computer Society Press.
-This style guide now has several important modifications (for example, you are no longer warned against the use of sticky tape to attach your artwork to the paper), so all authors should read this new version.
+Mental illness is one of the most important diseases of people, and depression is the most common psychological disease ~\cite{world2017depression,bhugra2004globalisation,rao2008understanding}. 
+According to World Health Organization (WHO), the cases of depression is rising by more than 25\% around the world during Covid-19.
+With the increase of academic stress and social pressure, the age of depressed people is becoming younger and younger.
+Many teenagers suffer from depression, which seriously affects the health of teenagers and their families.
+Although suffering from depression does not directly lead to death, but many Major Depressive Disorder (MDD) people have the suicide tendency~\cite{eisenberg2007prevalence,bergfeld2018treatment,hemming2019alexithymia}.
+In statistical surveys, the probability of suicide in depressed people is around 10-15\%, which has great impact on personal wellbeing and social stability.
 
 %-------------------------------------------------------------------------
-\subsection{Language}
+%\subsection{Language}
 
-All manuscripts must be in English.
+%{\bf There will be no extra page charges for \confName\ \confYear.}
 
-\subsection{Dual submission}
-
-Please refer to the author guidelines on the \confName\ \confYear\ web page for a
-discussion of the policy on dual submissions.
-
-\subsection{Paper length}
-Papers, excluding the references section, must be no longer than eight pages in length.
-The references section will not be included in the page count, and there is no limit on the length of the references section.
-For example, a paper of eight pages with two pages of references would have a total length of 10 pages.
-{\bf There will be no extra page charges for \confName\ \confYear.}
-
-Overlength papers will simply not be reviewed.
-This includes papers where the margins and formatting are deemed to have been significantly altered from those laid down by this style guide.
-Note that this \LaTeX\ guide already sets figure captions and references in a smaller font.
-The reason such papers will not be reviewed is that there is no provision for supervised revisions of manuscripts.
-The reviewing process cannot determine the suitability of the paper for presentation in eight pages if it is reviewed in eleven.
+Because of the high prevalence of depression and high suicide rate, it is becoming increasingly important to have an effective diagnostic protocol to detect depression.
+However, the clinical diagnosis of depression is cumbersome.
+People should go to designated hospitals or clinics, and professional doctors need to make comprehensive judgments based on disease history, clinical symptoms, degree of disease, physical condition and laboratory tests~\cite{faust1988expert}.
+Moreover, some people are resistant and do not cooperate with diagnosis or treatment, which missing the best time for treatment.
 
 %-------------------------------------------------------------------------
-\subsection{The ruler}
-The \LaTeX\ style defines a printed ruler which should be present in the version submitted for review.
-The ruler is provided in order that reviewers may comment on particular lines in the paper without circumlocution.
-If you are preparing a document using a non-\LaTeX\ document preparation system, please arrange for an equivalent ruler to appear on the final output pages.
-The presence or absence of the ruler should not change the appearance of any other content on the page.
-The camera-ready copy should not contain a ruler.
-(\LaTeX\ users may use options of cvpr.sty to switch between different versions.)
 
-Reviewers:
-note that the ruler measurements do not align well with lines in the paper --- this turns out to be very difficult to do well when the paper contains many figures and equations, and, when done, looks ugly.
-Just use fractional references (\eg, this line is $087.5$), although in most cases one would expect that the approximate location will be adequate.
+\begin{figure}[t]
+  \centering
+  %\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+   \includegraphics[width=1.0\linewidth]{figures/example.png}
 
-\subsection{Paper ID}
-Make sure that the Paper ID from the submission system is visible in the version submitted for review (replacing the ``*****'' you see in this document).
-If you are using the \LaTeX\ template, \textbf{make sure to update paper ID in the appropriate place in the tex file}.
+   \caption{Example of dataset: Different gait representations of the same person from multiple cameras and clothes. 
+   The rows show subject with multiple views from different cameras. The columns show subject with 3 different clothes.
+   }
+   \label{Introduction}
+\end{figure}
 
+%-------------------------------------------------------------------------
+%\subsection{The ruler}
+
+The gait of person is stable, and it’s difficult to disguise or change.
+Many researches shows that the fluctuations in mood can lead the changes in gait specially in some gait characteristics, such as the number of arm swings, stride length and walking speed~\cite{hicheur2013perception,montepare1987identification,roether2009critical,venture2014recognizing,gross2012effort,janssen2008recognition,kang2016effect,li2016emotion,li2016identifying,bhattacharya2020step} .
+Negative emotions are the basic manifestation in depressed people, and research showed that the analysis of abnormal gait can also be applied to the recognition of depression ~\cite{michalak2009embodiment}.
+People with depression will be accompanied by decreased vertical head movement, reduced limb range of motion, and slower pace ~\cite{sloman1982gait,lemke2000spatiotemporal,bovi2011multiple,radovanovic2014gait,zhao2019see,yuan2018depression,fang2019depression,jing2019different}.
+Compared with traditional psychological measurement methods, the mental disease identification method based on gait data has the advantages of non-interference, traceability, automation and so on, which can effectively improve the accuracy of mental disease detection.
+Gait analysis is a mature tool for quantitative evaluation of depression, which can provide auxiliary functions such as diagnosis, treatment, evaluation and disease progress monitoring ~\cite{baker2016gait,wang2020gait,lu2021new,wang2021detecting,yang2022data}.
+
+%-------------------------------------------------------------------------
+
+Considering the feasibility and advantages of gait recognition in depression, we propose a hypothesis to detect depressed people based on gait information.
+Specifically, the gait of subject is captured by cameras, and then the diagnostic model detects whether people are at risk of depression.
+
+%-------------------------------------------------------------------------
+
+To facilitate the study of gait based auxiliary diagnosis of depression, we build the gait-depression dataset, short for D-gait, which is a large-scale and high-quality gait dataset.
+The D-gait dataset is collected from students with multiple cameras and clothes as shown in Fig1.
+We have done many experiments on this dataset using different modal identification algorithms, and the results show that the existing algorithms can’t complete this task well, and the performance still needs to be improved.
+
+%-------------------------------------------------------------------------
+
+In summary, the contributions of this paper are as follows:
+\begin{itemize}
+\item We build the first public gait based auxiliary diagnosis of depression dataset, named D-Gait, which provides the depression information of gait collected from students with multiple views and clothes.
+
+\item We propose a framework for auxiliary depression diagnosis based on gait data with different modes.
+Results indicate that the D-gait is necessary and effective for auxiliary depression diagnosis with students.
+Besides, diagnose depression based on gait is a very challenging task for current approaches and still needs to be improved.
+
+\item We make the thorough analysis on the relationship between gait and depression.
+\end{itemize}
+
+%-------------------------------------------------------------------------
 \subsection{Mathematics}

### 2022-10-17 cvpr2023/latex/PaperForReview - 副本.tex
Add files via upload

@@
 To facilitate the study of gait based auxiliary diagnosis of depression, we build the gait-depression dataset, short for D-gait, which is a large-scale and high-quality gait dataset.
-The D-gait dataset is collected from students with multiple cameras and clothes as shown in Fig1.
+The D-gait dataset is collected from students with multiple cameras and clothes as shown in Fig \ref{Introduction}.
 We have done many experiments on this dataset using different modal identification algorithms, and the results show that the existing algorithms can’t complete this task well, and the performance still needs to be improved.
@@
 
-%-------------------------------------------------------------------------
-\subsection{Mathematics}
+\section{Related Work}
+\label{sec:intro}
 
-Please number all of your sections and displayed equations as in these examples:
-\begin{equation}
-  E = m\cdot c^2
-  \label{eq:important}
-\end{equation}
-and
-\begin{equation}
-  v = a\cdot t.
-  \label{eq:also-important}
-\end{equation}
-It is important for readers to be able to refer to any particular equation.
-Just because you did not refer to it in the text does not mean some future reader might not need to refer to it.
-It is cumbersome to have to use circumlocutions like ``the equation second from the top of page 3 column 1''.
-(Note that the ruler will not be present in the final copy, so is not an alternative to equation numbers).
-All authors will benefit from reading Mermin's description of how to write mathematics:
-\url{http://www.pamitc.org/documents/mermin.pdf}.
+In this section, we discuss two related aspects: gait data collection and current research on depression risk recognition based on gait.
 
-\subsection{Blind review}
+\subsection{Gait Data Collection }
 
-Many authors misunderstand the concept of anonymizing for blind review.
-Blind review does not mean that one must remove citations to one's own work---in fact it is often impossible to review a paper unless the previous citations are known and available.
+A high-quality dataset is essential for training and evaluating gait-based depression risk recognition algorithms.
+However, no publicly accessible datasets are available at this time.
+So we concentrate on the gait data gathering techniques used in the current study, which may be divided into three primary categories: motion capture systems, walkways with embedded pressure sensors, and Kinect sensors.
+(1)
+Motion capture systems: Motion capture systems, like Vicon~\cite{michalak2009embodiment}, are practical recording techniques that use infrared cameras to capture body movements indicated by reflective markers~\cite{bovi2011multiple}.
+These systems monitor spatial and physical movements and deliver highly accurate data at 100 and 200 Hz sampling rates.
+They do, however, cost a lot and require professional surgery.
+Additionally, they are restricted to lab environments, so the information that comes from them might not accurately represent gait in a real-world scenario~\cite{cho2018evaluation}.
+(2)Walkway with embedded pressure sensors:
+The walkway system is a portable 'carpet' walkway with pressure sensors embedded within its length~\cite{webster2005validity,menz2004reliability,bilney2003concurrent}.
+Subjects walk over the carpet without the encumbrance of wires or markers, and data can be quickly and easily obtained for each step within the entire gait trial~\cite{lemke2000spatiotemporal}.
+GAITRite~\cite{gabel2015dual,brandler2012depressive}is the most commonly used electronic footpath system, offering the advantage of portability but with a low sampling frequency of 80 Hz and relatively low sensor density.
+%Variables that can be quantified include walking speed, cadence, step length, single and double limb support duration and stride width for individual steps and the step sequence.
+(3)Kinect sensors: Kinect equipped with depth and infrared sensors may detect distance data in space, estimate 3D coordinate data, and provide joint-specific coordinate data depending on the joint body structure.
+Currently, Kinect capture is the only data source used in machine learning-based gait depression risk detection investigations.
+However, the skeleton data supplied by the Kinect is of poor quality.
+Due to the Kinect's detection range, the quality of gait images captured when people were too close to or too far from the device was similarly poor.
+Worse yet, in all of the experiments, only frontal and lateral data were included, but gait data from all angles must be considered in real-world situations~\cite{shao2021multi}.
+As a result, in our study, we investigated the gait data capture method from various angles and extracted high-quality skeletal data using an advanced posture estimation algorithm.
 
-Blind review means that you do not use the words ``my'' or ``our'' when citing previous work.
-That is all.
-(But see below for tech reports.)
+\subsection{Gait-based depression risk recognition}
 
-Saying ``this builds on the work of Lucy Smith [1]'' does not say that you are Lucy Smith;
-it says that you are building on her work.
-If you are Smith and Jones, do not say ``as we show in [7]'', say ``as Smith and Jones show in [7]'' and at the end of the paper, include reference 7 as you would any other cited work.
+Together, advanced gait acquisition techniques and machine learning methodologies have contributed to developing the gait-based depression risk recognition.
+There are two types of current research methodologies: traditional machine learning-based and deep learning-based approaches.
 
-An example of a bad paper just asking to be rejected:
-\begin{quote}
-\begin{center}
-    An analysis of the frobnicatable foo filter.
-\end{center}
+\subsubsection{Gait depression risk recognition using traditional machine learning}
+Previous research found that the gait features of depressed patients were significantly different from normal individuals~\cite{sloman1982gait,lemke2000spatiotemporal}.
+Therefore, in the study of gait-based depression risk, the main work was to manually extract the gait features associated with depression for better performance.
+Meanwhile, traditional machine learning algorithms such as support vector machine (SVM)~\cite{wang2021detecting,li2021simple,fang2019depression,lu2022postgraduate,yuan2018depression}, logistic regression~\cite{li2021simple,fang2019depression}, and random forest~\cite{wang2021detecting,fang2019depression,lu2022postgraduate} were used in the subsequent classification and detection.
+For example, Wang~\cite{wang2021detecting} extracted spatio-temporal, time-domain, and frequency-domain features of gait and used SVM to construct a machine learning model to further explore the contribution of different types of features.
+The results showed that the model trained using only time- and frequency-domain features demonstrated the same best performance compared to the model trained using all the features.
+In recent studies, scholars have been devoted to examining new gait characteristics and applying traditional machine learning models for detection, and the accuracy has been steadily enhanced.
+However, traditional machine learning algorithms were limited in analysing raw natural data.
+They could not articulate sophisticated functions, making solving more complex natural signal processing challenges impossible.
 
-   In this paper we present a performance analysis of our previous paper [1], and show it to be inferior to all previously known methods.
-   Why the previous paper was accepted without this analysis is beyond me.
+\subsubsection{Gait depression risk recognition using deep learning}
 
-   [1] Removed for blind review
-\end{quote}
-
-An example of an acceptable paper:
-\begin{quote}
-\begin{center}
-     An analysis of the frobnicatable foo filter.
-\end{center}
-
-   In this paper we present a performance analysis of the  paper of Smith \etal [1], and show it to be inferior to all previously known methods.
-   Why the previous paper was accepted without this analysis is beyond me.
-
-   [1] Smith, L and Jones, C. ``The frobnicatable foo filter, a fundamental contribution to human knowledge''. Nature 381(12), 1-213.
-\end{quote}
-
-If you are making a submission to another conference at the same time, which covers similar or overlapping material, you may need to refer to that submission in order to explain the differences, just as you would if you had previously published related work.
-In such cases, include the anonymized parallel submission~\cite{Authors14} as supplemental material and cite it as
-\begin{quote}
-[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324, Supplied as supplemental material {\tt fg324.pdf}.
-\end{quote}
-
-Finally, you may feel you need to tell the reader that more details can be found elsewhere, and refer them to a technical report.
-For conference submissions, the paper must stand on its own, and not {\em require} the reviewer to go to a tech report for further details.
-Thus, you may say in the body of the paper ``further details may be found in~\cite{Authors14b}''.
-Then submit the tech report as supplemental material.
-Again, you may not assume the reviewers will read this material.
-
-Sometimes your paper is about a problem which you tested using a tool that is widely known to be restricted to a single institution.
-For example, let's say it's 1969, you have solved a key problem on the Apollo lander, and you believe that the CVPR70 audience would like to hear about your
-solution.
-The work is a development of your celebrated 1968 paper entitled ``Zero-g frobnication: How being the only people in the world with access to the Apollo lander source code makes us a wow at parties'', by Zeus \etal.
-
-You can handle this paper like any other.
-Do not write ``We show how to improve our previous work [Anonymous, 1968].
-This time we tested the algorithm on a lunar lander [name of lander removed for blind review]''.
-That would be silly, and would immediately identify the authors.
-Instead write the following:
-\begin{quotation}
-\noindent
-   We describe a system for zero-g frobnication.
-   This system is new because it handles the following cases:
-   A, B.  Previous systems [Zeus et al. 1968] did not  handle case B properly.
-   Ours handles it by including a foo term in the bar integral.
-
-   ...
-
-   The proposed system was integrated with the Apollo lunar lander, and went all the way to the moon, don't you know.
-   It displayed the following behaviours, which show how well we solved cases A and B: ...
-\end{quotation}
-As you can see, the above text follows standard scientific convention, reads better than the first version, and does not explicitly name you as the authors.
-A reviewer might think it likely that the new paper was written by Zeus \etal, but cannot make any decision based on that guess.
-He or she would have to be sure that no other authors could have been contracted to solve problem B.
-\medskip
-
-\noindent
-FAQ\medskip\\
-{\bf Q:} Are acknowledgements OK?\\
-{\bf A:} No.  Leave them for the final copy.\medskip\\
-{\bf Q:} How do I cite my results reported in open challenges?
-{\bf A:} To conform with the double-blind review policy, you can report results of other challenge participants together with your results in your paper.
-For your results, however, you should not identify yourself and should not mention your participation in the challenge.
-Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\
-
-\begin{figure}[t]
-  \centering
-  \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
-
-   \caption{Example of caption.
-   It is set in Roman so that mathematics (always set in Roman: $B \sin A = A \sin B$) may be included without an ugly clash.}
-   \label{fig:onecol}
-\end{figure}
-
-\subsection{Miscellaneous}
-
-\noindent
-Compare the following:\\
-\begin{tabular}{ll}
- \verb'$conf_a$' &  $conf_a$ \\
- \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
-\end{tabular}\\
-See The \TeX book, p165.
-
-The space after \eg, meaning ``for example'', should not be a sentence-ending space.
-So \eg is correct, {\em e.g.} is not.
-The provided \verb'\eg' macro takes care of this.
-
-When citing a multi-author paper, you may save space by using ``et alia'', shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word).
-If you use the \verb'\etal' macro provided, then you need not worry about double periods when used at the end of a sentence as in Alpher \etal.
-However, use it only when there are three or more authors.
-Thus, the following is correct:
-   ``Frobnication has been trendy lately.
-   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
-   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''
-
-This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...'' because reference~\cite{Alpher03} has just two authors.
-
-% Update the cvpr.cls to do the following automatically.
-% For this citation style, keep multiple citations in numerical (not
-% chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
-% \cite{Alpher02,Alpher03,Authors14}.
-
-\begin{figure*}
-  \centering
-  \begin{subfigure}{0.68\linewidth}
-    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-    \caption{An example of a subfigure.}
-    \label{fig:short-a}
-  \end{subfigure}
-  \hfill
-  \begin{subfigure}{0.28\linewidth}
-    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-    \caption{Another example of a subfigure.}
-    \label{fig:short-b}
-  \end{subfigure}
-  \caption{Example of a short caption, which should be centered.}
-  \label{fig:short}
-\end{figure*}
-
-%------------------------------------------------------------------------
-\section{Formatting your paper}
-\label{sec:formatting}
-
-All text must be in a two-column format.
-The total allowable size of the text area is $6\frac78$ inches (17.46 cm) wide by $8\frac78$ inches (22.54 cm) high.
-Columns are to be $3\frac14$ inches (8.25 cm) wide, with a $\frac{5}{16}$ inch (0.8 cm) space between them.
-The main title (on the first page) should begin 1 inch (2.54 cm) from the top edge of the page.
-The second and following pages should begin 1 inch (2.54 cm) from the top edge.
-On all pages, the bottom margin should be $1\frac{1}{8}$ inches (2.86 cm) from the bottom edge of the page for $8.5 \times 11$-inch paper;
-for A4 paper, approximately $1\frac{5}{8}$ inches (4.13 cm) from the bottom edge of the
-page.
-
-%-------------------------------------------------------------------------
-\subsection{Margins and page numbering}
-
-All printed material, including text, illustrations, and charts, must be kept
-within a print area $6\frac{7}{8}$ inches (17.46 cm) wide by $8\frac{7}{8}$ inches (22.54 cm)
-high.
-%
-Page numbers should be in the footer, centered and $\frac{3}{4}$ inches from the bottom of the page.
-The review version should have page numbers, yet the final version submitted as camera ready should not show any page numbers.
-The \LaTeX\ template takes care of this when used properly.
-
-%-------------------------------------------------------------------------
-\subsection{Type style and fonts}
-
-Wherever Times is specified, Times Roman may also be used.
-If neither is available on your word processor, please use the font closest in
-appearance to Times to which you have access.
-
-MAIN TITLE.
-Center the title $1\frac{3}{8}$ inches (3.49 cm) from the top edge of the first page.
-The title should be in Times 14-point, boldface type.
-Capitalize the first letter of nouns, pronouns, verbs, adjectives, and adverbs;
-do not capitalize articles, coordinate conjunctions, or prepositions (unless the title begins with such a word).
-Leave two blank lines after the title.
-
-AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
-and printed in Times 12-point, non-boldface type.
-This information is to be followed by two blank lines.
-
-The ABSTRACT and MAIN TEXT are to be in a two-column format.
-
-MAIN TEXT.
-Type main text in 10-point Times, single-spaced.
-Do NOT use double-spacing.
-All paragraphs should be indented 1 pica (approx.~$\frac{1}{6}$ inch or 0.422 cm).
-Make sure your text is fully justified---that is, flush left and flush right.
-Please do not place any additional blank lines between paragraphs.
-
-Figure and table captions should be 9-point Roman type as in \cref{fig:onecol,fig:short}.
-Short captions should be centred.
-
-\noindent Callouts should be 9-point Helvetica, non-boldface type.
-Initially capitalize only the first word of section titles and first-, second-, and third-order headings.
-
-FIRST-ORDER HEADINGS.
-(For example, {\large \bf 1. Introduction}) should be Times 12-point boldface, initially capitalized, flush left, with one blank line before, and one blank line after.
-
-SECOND-ORDER HEADINGS.
-(For example, { \bf 1.1. Database elements}) should be Times 11-point boldface, initially capitalized, flush left, with one blank line before, and one after.
-If you require a third-order heading (we discourage it), use 10-point Times, boldface, initially capitalized, flush left, preceded by one blank line, followed by a period and your text on the same line.
-
-%-------------------------------------------------------------------------
-\subsection{Footnotes}
-
-Please use footnotes\footnote{This is what a footnote looks like.
-It often distracts the reader from the main flow of the argument.} sparingly.
-Indeed, try to avoid footnotes altogether and include necessary peripheral observations in the text (within parentheses, if you prefer, as in this sentence).
-If you wish to use a footnote, place it at the bottom of the column on the page on which it is referenced.
-Use Times 8-point type, single-spaced.
-
-%-------------------------------------------------------------------------
-\subsection{Cross-references}
-
-For the benefit of author(s) and readers, please use the
-{\small\begin{verbatim}
-  \cref{...}
-\end{verbatim}}  command for cross-referencing to figures, tables, equations, or sections.
-This will automatically insert the appropriate label alongside the cross-reference as in this example:
-\begin{quotation}
-  To see how our method outperforms previous work, please see \cref{fig:onecol} and \cref{tab:example}.
-  It is also possible to refer to multiple targets as once, \eg~to \cref{fig:onecol,fig:short-a}.
-  You may also return to \cref{sec:formatting} or look at \cref{eq:also-important}.
-\end{quotation}
-If you do not wish to abbreviate the label, for example at the beginning of the sentence, you can use the
-{\small\begin{verbatim}
-  \Cref{...}
-\end{verbatim}}
-command. Here is an example:
-\begin{quotation}
-  \Cref{fig:onecol} is also quite important.
-\end{quotation}
-
-%-------------------------------------------------------------------------
-\subsection{References}
-
-List and number all bibliographical references in 9-point Times, single-spaced, at the end of your paper.
-When referenced in the text, enclose the citation number in square brackets, for
-example~\cite{Authors14}.
-Where appropriate, include page numbers and the name(s) of editors of referenced books.
-When you cite multiple papers at once, please make sure that you cite them in numerical order like this \cite{Alpher02,Alpher03,Alpher05,Authors14b,Authors14}.
-If you use the template as advised, this will be taken care of automatically.
-
-\begin{table}
-  \centering
-  \begin{tabular}{@{}lc@{}}
-    \toprule
-    Method & Frobnability \\
-    \midrule
-    Theirs & Frumpy \\
-    Yours & Frobbly \\
-    Ours & Makes one's heart Frob\\
-    \bottomrule
-  \end{tabular}
-  \caption{Results.   Ours is better.}
-  \label{tab:example}
-\end{table}
-
-%-------------------------------------------------------------------------
-\subsection{Illustrations, graphs, and photographs}
-
-All graphics should be centered.
-In \LaTeX, avoid using the \texttt{center} environment for this purpose, as this adds potentially unwanted whitespace.
-Instead use
-{\small\begin{verbatim}
-  \centering
-\end{verbatim}}
-at the beginning of your figure.
-Please ensure that any point you wish to make is resolvable in a printed copy of the paper.
-Resize fonts in figures to match the font in the body text, and choose line widths that render effectively in print.
-Readers (and reviewers), even of an electronic copy, may choose to print your paper in order to read it.
-You cannot insist that they do otherwise, and therefore must not assume that they can zoom in to see tiny details on a graphic.
-
-When placing figures in \LaTeX, it's almost always best to use \verb+\includegraphics+, and to specify the figure width as a multiple of the line width as in the example below
-{\small\begin{verbatim}
-   \usepackage{graphicx} ...
-   \includegraphics[width=0.8\linewidth]
-                   {myfile.pdf}
-\end{verbatim}
-}
-
-%-------------------------------------------------------------------------
-\subsection{Color}
-
-Please refer to the author guidelines on the \confName\ \confYear\ web page for a discussion of the use of color in your document.
-
-If you use color in your plots, please keep in mind that a significant subset of reviewers and readers may have a color vision deficiency; red-green blindness is the most frequent kind.
-Hence avoid relying only on color as the discriminative feature in plots (such as red \vs green lines), but add a second discriminative feature to ease disambiguation.
-
-%------------------------------------------------------------------------
-\section{Final copy}
-
-You must include your signed IEEE copyright release form when you submit your finished paper.
-We MUST have this form before your paper can be published in the proceedings.
-
-Please direct any questions to the production editor in charge of these proceedings at the IEEE Computer Society Press:
-\url{https://www.computer.org/about/contact}.
+There are two primary types of deep learning-based depression risk assessment based on the input modality of the network: skeleton~\cite{yang2022data} and multi-modal (skeleton and silhouette).
+The quality of the joint coordinate data, which is quickly impacted by surroundings such as distance, light, and other factors, is the key to skeleton studies~\cite{cippitelli2016human}.
+In complex settings, the assessment of the skeleton is inaccurate.
+Cross-view recognition is the most challenging aspect of silhouettes studies because the results of identification vary significantly between different perspectives~\cite{wu2016comprehensive}.
+By taking advantage of the correlation between each modality, multi-modal fusion can enhance the model's generalization and recognition ability.
+To detect depression, Shao~\cite{shao2021multi} presented a hybrid fusion model with skeleton and silhouette.
+For skeleton data, they proposed an effective feature set. As for RGB images, they extracted human silhouettes
+and generated Gait Engery Image(GEI).
+The experimental results imply that the proposed method leveraging the complementarity gained a higher accuracy.
+However, both the feature extraction of the skeleton alone and the generation of GEI with  silhouettes suffer from variable degrees of information loss.
+Instead, employing an end-to-end deep architecture to push the original signal into the model for learning may produce unanticipated results.
+The benefit of end-to-end deep architecture is that it does not require researchers to possess a priori knowledge, and the deep network can learn better features and produce more accurate classification results.
+However, there are drawbacks to end-to-end deep systems, such as limited support for large-scale data.
 

### 2022-11-01 cvpr2023/latex/PaperForReview - 副本.tex
Update PaperForReview - 副本.tex
Add files via upload

@@
 %\title{\LaTeX\ Author Guidelines for \confName~Proceedings}
-\title{A Dataset for Auxiliary Depression Diagnosis based on Gait}
+\title{D-Gait: A Dataset for Auxiliary Depression Diagnosis based on Gait}
 
@@
 
+\section{D-Gait Dataset}
+\begin{figure}[t]
+  \centering
+  %\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+   \includegraphics[width=1.0\linewidth]{figures/pre-processing02.jpg}
+
+   \caption{ Pre-processing of D-Gait data generates silhouette images.
+   }
+   \label{pre-processing}
+\end{figure}
+\subsection{Data Pre-processing}
+
+After obtaining the raw gait video data, we further pre-process them to prepare the required input data for  deep learning-based depression risk detection methods.
+As shown in Fig~\ref{pre-processing}, we first crop the videos with assistance of a multi-object tracking algorithm such that each cropped video clip contains only one walking subject of interests and one gait sequence refers to the video clip of a subject when he/she walks along a straight line towards one direction.
+Afterwards,  a real-time instance segmentation algorithm, to obtain the human silhouettes, and then normalize and align the silhouette data.
+
+\subsection{Data cleaning}
+
+The three primary stages of data cleaning are noise removal, frame filtering, and Forward and backward sequence splitting. Below, we'll introduce them one at a time.
+(1) Noise removal: During data collection, the camera takes pictures of places that are not being used for data acquisition, such as irrelevant people who are not the subjects.
+They should be deleted because they may damage the quality of the data.
+(2) Frame filtering: When subjects enter and exit the data collection area, there will be duplicate information, such as changing clothes, as well as an action of turning when subjects reach the end point.
+Such information is also unwanted and they should be removed.
+(3) Forward and backward sequence splitting: During data acquisition, the subjects walk a round trip in the effective area of data acquisition, so there are two image sequences facing the camera or back to the camera, which need to be split and processed.
+It takes 10 researchers working for 2 weeks for this tremendous work, and we hope the proposed D-Gait benchmark would facilitate future research of gait depression risk detection.
+Note that for privacy concerns, we will first release the pre-processed gait data to the public.
+
+\subsection{Annotations}
+
+To assess the degree of depression of the subjects, we used three internationally used scales, Self-Rating Depression Scale (SDS), Patient Health Questionnaire-9 (PHQ-9), and Generalized Anxiexy Disorde-7 (GAD-7).
+The subjects were divided into two groups according to their scores: the non-depressed group and the scored depressed group.
+In order to ensure the validity of the experimental data, we summarized the classification criteria of the scales used in the relevant literature and set the inclusion criteria of the enrolled subjects by combining the specific situation of our data, as described in Table~\ref{scale}.
+
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+\begin{table}[]
+\caption{The scoring criteria of the selected subjects}
+\label{scale}
+\setlength{\tabcolsep}{3.5mm}{
+\begin{tabular}{@{}c|c|c|c@{}}
+\toprule
+\textbf{Paper} & \textbf{PHQ-9} & \textbf{SDS} & \textbf{GAD-7} \\ \midrule
+Fang~\cite{fang2019depression}  & $score \geq 5$  & $score \geq 50$  & $score \geq 5$             \\
+Yang~\cite{yang2022data}        & $score \geq 10$ & $score \geq 60$ & -              \\
+Lu~\cite{lu2021new}             & $score \geq 10$ & $score \geq 60$ & -              \\
+Wang~\cite{wang2020gait}        & $score \geq 10$ & $score \geq 60$ & -              \\
+Daly~\cite{daly2021depression}  & $score \geq 10$ & -      & -              \\
+Jing~\cite{jing2019different}   & $score \geq 10$ & -                  & $score \geq 10$       \\
+Zhao~\cite{zhao2019see}         & $score \geq 10$ & -      & $score \geq 10$       \\
+Choi~\cite{choi2020depression}  & $score \geq 10$ & -      & $score \geq 10$       \\
+Hyland~\cite{hyland2020anxiety} & $score \geq 10$ & -      & $score \geq 10$       \\
+\textbf{Our}  & $score \geq 10$ & $score \geq 40$ & $score \geq 10$ \\ \bottomrule
+\end{tabular}}
+\end{table}
+
+The non-depressed group (PHQ-9: mean = 0.92, SD = 1.26; SDS: mean = 6.4, SD = 2.14; GAD-7: mean=0.51, SD=0.95) consisted of 200 individuals
+(M: 122, F: 78), whose scores were in the healthy range of both the PHQ-9, SDS, and GAD-7.
+The scored-depressed group (PHQ-9: mean = 11.52, SD = 3.24; SDS: mean = 30.52, SD = 6.53; GAD-7: mean=9.40, SD=3.12) contained 200 (M: 92, F: 108) participants.
+%The criteria for recruiting the scored-depressed group were that the candidates must be assessed as depression in both the PHQ-9 or SDS.
+Candidates for the scored-depressed group had to score depressed on the PHQ-9, SDS, or GAD-7 in order to be included.
+In addition, the score had to reach a moderate level in at least one of them ( PHQ-9 score $\geq$ 10 or SDS score $\geq$ 40 or GAD-7 score $\geq$ 10).
+Basic information about the subjects is provided in Table~\ref{score}.
+
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+\begin{table}[]
+\caption{Basic information of the scored-depressed and non-depressed groups.}
+\label{score}
+\setlength{\tabcolsep}{1mm}{
+\begin{tabular}{@{}c|cc@{}}
+\toprule
+\textbf{ } & \textbf{Scored-depressed} & \textbf{Non-depressed} \\ \midrule
+Cases              & 200                       & 200                    \\
+Sex (M:F)           & 92:108                    & 122:78                 \\
+PHQ-9 ($means \pm SD$) & $11.52 \pm 3.24$          & $0.92 \pm 1.26$              \\
+SDS ($means \pm SD$)   & $30.52 \pm 6.53$          & $6.40 \pm 2.14$              \\
+GAD-7 ($means \pm SD$) & $9.40 \pm 3.12$           & $0.51 \pm 0.95$              \\ \bottomrule
+\end{tabular}}
+\end{table}
+
 %%%%%%%%% REFERENCES

### 2022-11-01 cvpr2023/latex/PaperForReview - 副本.tex
Add files via upload

@@
 \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%% lxt start
+Our D-gait dataset introduces a new challenging benchmark for gait-based depression detection.
+This section presents the key challenges of data collection and details of our data structure and statistical characteristics.
+Moreover, we summarize the preprocessing of our dataset for further studies.
+
+\subsection{Key Challenge}
+building such a complex and large-scale dataset brings a series of unprecedented challenges, including:
+1) How to collect data?
+The gait data in traditional depression detection are usually collected by ground sensors or Kinect devices, which obtain the gait information of subjects, such as simple features (stride length, gait speed, etc.) or human joint coordinates.
+These methods require subjects to wear professional equipment, and cannot collect image information about gait.
+Instead, we collect video data from multiple cameras of subject's walking, and process it to get the silhouette and skeleton information.
+2) How to define depressed subjects?
+The traditional diagnosis of depression basically needs to be tested by scale, then followed by physical examination and professional diagnosis.
+The data of patients with depression may have privacy problems and are difficult to collect.
+As mentioned, before collecting the gait data, we tested the subjects with scale, and divided the depressed and normal subjects according to the scores.
+At the same time, we take three commonly used scales to ensure reliability of the results, and divided the depressed and normal subjects according to their comprehensive scores.
+3) How to ensure data quality?
+When collecting data in the real scene, it contains a lot of noises due to the complexity of the background.
+In order to solve this problem, we use the green screen to build experimental scenes around the collection area to minimize background interference.
+
+\subsection{Dataset Construction}
+Data preparation:
+our procedure for data collection takes the following steps.
+Firstly, we collect the basic information (name, age, sex...) of the subjects and the scores of the three depression scales.
+Then, we collect gait data of subjects through cameras, and process the data to obtain silhouette image.
+Finally, through the analysis of the scale results, we develop a label classification standard and divide 400 subjects into 200 depression group and 200 normal control group.
+
+Data composition:
+our dataset collects gait data of teenagers.
+All subjects know the purpose of data collection and allow us to use their data for research.
+The age range of subjects is 17-25 years old, and the male to female ratio is about 5:5.
+During the acquisition process, each subject is required to walk back and forth along the fixed route so that the camera can capture their gait data.
+
+Next, we introduce in detail the gait data acquisition process.
+The horizontal distance of the walking route in D-gait is about 6 meters.
+Each subject changed their clothes twice and walked along for three times.
+During the acquisition, 8 groups of cameras were distributed on one side and each group of cameras was 2.5 and 3.5 meters high respectively.
+During the collection, each subject needs to walk back and forth.
+Through the walking route, collect the gait sequence of each subject under different angles and clothes.
+
+\begin{figure}[t]
+  \centering
+  %\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+   \includegraphics[width=1.0\linewidth]{figures/Data format.png}
+
+   \caption{Data format.
+   }
+   \label{Data format}
+\end{figure}
+
+Data format:
+D-gait contains gait data of different types of clothes and multiple views, among which, the clothing type includes a backpack and two sets of normal clothes.
+The shooting angle includes 16 angles in the range of 0-180° and the front and back of each angle as shown in Fig~\ref{Data format}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%% lxt end
 \subsection{Data Pre-processing}
@@
 Sex (M:F)           & 92:108                    & 122:78                 \\
+Age ($M\pm SD$)        & $19\pm 1.032 $          & $ 20\pm 1.130  $      \\
 PHQ-9 ($means \pm SD$) & $11.52 \pm 3.24$          & $0.92 \pm 1.26$              \\
